\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-05 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
small adding in data-intensive software part concerning complexity
small change definition intuition correlation in data-intensive software part

The second package concerns correlations. Roughly speaking, a correlation is an operation with two seismograms that provides the coherence between the both signal (for a given time windows). Moreover, it represents, in some favorables cases, a new virtual seismogram (it converges to the Green's function). Thus, the code computes all the correlations and provides an architecture of files that corresponds to all the couples of seismograms (for each date).

@@

These quadratic space complexity can be critical and lot of effort was made in order to optimize the computation in two direction. First we improve the computation of the fast fourier transform by pre-calculating some "good" combinations of small primes numbers. 
With this method, we improve of forty percent the time computation in the favorable cases.

>>>>

The second package concerns correlations. 
Roughly speaking, a correlation is an operation with two seismograms (for a given time windows) that provides the coherent part of the two seismograms 
(associated to the 2 stations) which is the seismic wave that propagates between the 2 stations.
Moreover, it represents, in some favorables cases, a new virtual seismogram (it converges to the Green's function). Thus, the code computes all the correlations and provides an architecture of files that corresponds to all the couples of seismograms (for each date).

@@

Note that the space complexity is linear for seismograms processing but quadratic for the correlations. We have therefore to store the seismograms processing before compute the correlation in order to benefit of the good complexity.
These quadratic space complexity can be critical and lot of effort was made in order to optimize the computation in two direction. First we improve the computation of the fast fourier transform by pre-calculating some "good" combinations of small primes numbers. 
With this method, we improve of forty percent the time computation in the favorable cases.
